\chapter{Future work} \label{ch14}
This chapter considers future work and improvements of the final system described in chapter \ref{ch10}. The Fourier transform is a rather old and well-known method of frequency analysis, and the STFT provides a fine method of representing and analysing a signal in both time and frequency. However, the relation between the resolutions of time and frequencies in the STFT is lower bounded due to Heisenberg's uncertainty principle as described in theorem \ref{theo:Heisenberg}. The wavelet transform is a rather new and superior transform in signal processing compared to the Fourier transform.
\\ \\
Even though a window with a certain width that satisfies the relation $\sigma_t^2 \sigma_\omega^2 = \frac{1}{4}$ is chosen for the STFT, the width of the window cannot be changed during the analysis, which means that the Fourier transform is unsuitable to describe signals with both low and high frequencies. The wavelet transform is a different kind of transform, which is used to gain localised information in both frequency and time domains. While the Fourier transform converts a signal between the time and frequency domains, the coefficients of the wavelet transform represent details of the signal at different scale levels and their corresponding temporal location.
\begin{figure}[H]
\hspace*{-0.7cm}
\centering
\begin{tikzpicture}[scale = 0.19]
\draw (0,0) rectangle (16,16);
\foreach \x in {0,...,16}
	\draw (\x,0) -- (\x,16);
\node[rotate=90] at (-1.5,8) {Frequency};
\node at (8,18) {Time data};
\node at (8,-1.5) {Time};

\draw (20,0) rectangle (36,16);
\foreach \y in {0,...,16}
	\draw (20,\y) -- (36,\y);
\node[rotate=90] at (18.5,8) {Frequency};
\node at (28,18) {Fourier transform};
\node at (28,-1.5) {Time};

\draw (40,0) rectangle (56,16);
\foreach \y in {4,8,12}
	\draw (40,\y) -- (56,\y);
\foreach \x in {44,48,52}
	\draw (\x,0) -- (\x,16);
\node[rotate=90] at (38.5,8) {Frequency};
\node at (48,18) {STFT};
\node at (48,-1.5) {Time};

\draw (60,0.5) rectangle (76,16);
\foreach \y in {1,2,4,8}
	\draw (60,\y) -- (76,\y);
\foreach \x in {68}
	\draw (\x,1) -- (\x,16);
\foreach \x in {64,72}
	\draw (\x,2) -- (\x,16);	
\foreach \x in {62,66,70,74}
	\draw (\x,4) -- (\x,16);	
\foreach \x in {61,63,65,67,69,71,73,75}
	\draw (\x,8) -- (\x,16);		
	
\node[rotate=90] at (58.5,8) {Scale level};
\node at (68,18) {Wavelet transform};
\node at (68,-1.5) {Time};

\end{tikzpicture}
\caption{Comparisons of temporal and frequency locations in the Fourier and wavelet transforms.}
\label{fig:wave}
\end{figure}

This is summarised by figure \ref{fig:wave}, which shows 4 \textit{Heisenberg boxes}, where the area of each cell in each individual box are similar \cite{page 410, Wang}. The first box shows the signal in time with full time resolution but no frequency resolution; the second box shows the frequency spectrum achieved by the Fourier transform of the signal with full frequency resolution but no time resolution; the third box shows the STFT of the signal with a fixed window size and with equally (but not arbitrarily) good resolutions in time and frequency; and finally, the fourth box shows the wavelet transform of the signal with varying scale levels and their corresponding time resolutions. At a low scale level the window is wide, which gives a good frequency resolution but poor time resolution, and at a high scale level the window is narrow, which conversely gives poor frequency resolution but good time resolution. Furthermore, the area of each cell in the boxes for the STFT and the wavelet transform are determined by the width of the window and the particular wavelet being used, respectively \cite{pages 409-410, Wang} \cite{page 43-44, wave_tut}.

\input{sections/mainmatter/chapter_14/wavelet.tex}
\\ \\
Apart from a different type of transform, a verification of the temporal resolution of the spectrograms could be developed so as to be able to determine the specifications for a system capable of precisely placing notes in time. This would allow for a better assessment of the trade-off between temporal and spectral resolution as specified by Heisenberg's uncertainty principle. As of now only the spectral resolution of the spectrograms is assessed.
\\\\
The final system could be using different types of filters as described in the discussion in chapter \ref{ch12}. This would allow for optimisation of e.g. computational complexity.
\\\\

The peak detection algorithm could be supplemented with an algorithm to distinguish multiple tones played at once as well as different instruments. This would allow for an even broader scope of application, which naturally is highly desired by musicians all over the world, and big companies designing music notation softwares (such as the Sibelius software from Avid) are obviously working hard to design this kind of system. Therefore, the need for and range of future implications of the system described in this project are obviously huge.
