\chapter{Wavelet Analysis} \label{ch12}
The purpose of this chapter is merely to introduce the concept of wavelet analysis in order to apply it as an alternative to the Fourier transform described and applied in the former chapters.
\\ \\
As described in section \ref{sec:STFT}, the STFT is limited by Heisenberg's uncertainty principle. Moreover, even though a window with a certain width that satisfies the relation $\sigma_t^2 \sigma_\omega^2 = \frac{1}{4}$ is chosen, the width of the window cannot be changed during the analysis, which means that the Fourier transform is unsuitable to describe signals with both low and high frequencies. The wavelet transform is a different kind of transform, which is used to gain localized information in both frequency and time domains. While the Fourier transform converts a signal between the time and frequency domains, the coefficients of the wavelet transform represent details of the signal at different scale levels and their corresponding temporal location.
\\ \\
This is summarized by figure \martin{Lav figur og indsæt reference. \textregistered}, which shows 4 \textit{Heisenberg boxes}, where the area of each cell in each box are similar. The first box shows the signal in time with full time resolution but no frequency resolution; the second box shows the frequency spectrum achieved by the Fourier transform of the signal with full frequency resolution but no time resolution; the third box shows the STFT of the signal with a fixed window size and with equally (but not arbitrarily) good resolutions in time and frequency; and finally, the fourth box shows the wavelet transform of the signal with varying scale levels and their corresponding time resolutions. At a low scale level the window is wide, which gives a good frequency resolution but poor time resolution, and at a high scale level the window is narrow, which conversely gives poor frequency resolution but good time resolution. Furthermore, the area of each cell in the boxes for the STFT and the wavelet transform are determined by the width of the window and the particular wavelet being used, respectively \cite{pages 409-410, Wang} \cite{page 43-44, wave_tut}.

\input{sections/mainmatter/chapter_12/wavelet.tex}