\clearpage
\chapter{Supplementary files} \label{app:sup}
The folder \textit{G4-101a-P4} contains fundamental Python scripts used for this project. The scripts uses the audio files as inputs. 
\\
The folder is located at this link at GitHub: \url{https://github.com/TrineNyholm/G4-101a-P4/}.  \\
\\
Contents of the folder:
\begin{itemize}
\item[i.]\textit{Final\_application.py} \\
Script containing the final algorithm of the system developed in this project. The final test results can be recreated by this script. Furthermore, it is possible to print the results of each unit in the algorithm. Note that functions called in the script is defined in separate scripts described below.   

\item[ii.]\textit{fouriertransform.py}\\
Definse function to compute FFT, DFT, STFT, and dB representations.
 
\item[iii.] \textit{impulseresponse.py}\\
Defines functions to compute the impulse responses corresponding to lowpass, highpass, bandpass, and bandstop filters.
\item[iv.] \textit{windowfunctions.py}\\
Defines functions to compute the windows functions corresponding to the Bartlett, Hann, Hamming, Blackmann, and Kaiser windows. 
\item[v.] \textit{peak\_detection.py} \\
Defines the peak amplitude detection as a function.
\\
\\
Other scripts of interest:
\item[vi.] \textit{SNR\_variation.py} \\
Script for computing the test of varying SNR values, including plots.  
\item[vii.]\textit{spectrogram.py}\\
Script containing unit test of STFT involving generated test signal, including plots of spectrogram. 
\item[viii.] \textit{dbplots.py} \\
Computes dB plots of the Kaiser window with varying M and $\beta$ values. dB plots of the other windows can also be computed by changing the arguments.
\end{itemize}

To run the script in the folder the programming language \textit{Python 2.7} has to be used. This can be downloaded from: \url{https://www.python.org/download/releases/2.7/}. All scripts has to run in this exact folder as the folder contains the sound files in the folder \textit{Lydfiler}, which are imported in the Python scripts.