\section{Fourier series}
Functions can be represented as a linear combination of functions on the form $\sin nt$.
Or in other words linear combination of a oscillating function, sines, cosines or equivalently complex exponential.
\\\\
It can be an advantage to decompose functions, as a series or integral of "simpler" functions, to retrieve information.
\begin{align*}
	f(x) = \sum_{n=1}^\infty c_n f_n(x)\text{, or } f(x)= \int_{-\infty}^\infty g(u) h(u,x) du
\end{align*}
Information from a function $f(x)$ will, as an example be stored in the coefficient $\{c_n\}_{n=1}^\infty$.
The coefficients can easily be stored on a computer.
\\\\ 
Furthermore a function $f: \mathbb{R}\to\mathbb{R}$ (or $\mathbb{C}$) is called $2\pi$-periodic, if $f(\theta + 2\pi) = f(\theta), \forall\theta\in\mathbb{R}$

The idea of the Fourier series is using the above information to recreate a $2\pi$- periodic signal.\\
The Fourier series is defined as:
\begin{align*}
	f(t) &= a_0 + \sum_{n=1}^\infty(a_n \cos(n \omega t) + b_n \sin(n \omega t))\\
	&= \sum_{n=-\infty}^{\infty} c_n e^{n j\omega t} 
\end{align*}
The second part holds per Euler's formula:
\begin{align*}
	\cos(n(\theta) = \dfrac{e^{j n \theta} + e^{-j n \theta}}{2} \text{ and } \sin(n \theta) = \dfrac{e^{jn\theta}-e^{jn\theta}}{2j}
\end{align*}

It can be simpler to work with the complex exponential function, but working with the trigonometric functions $\cos$ and $\sin$ have there advantages. 
Like being real-valued and odd and even, for cosine and sine respectively.

\subsection{Calculation of the coefficient $c_n$}
It is a necessity to calculate the $c_n$ coefficient.
By the assumption that this can be done, and it's permissible to integrate the fourier series term by term: :\\
\\
To solve $c_n$ in the equation $f(t)= \sum_{n=-\infty}^{\infty} c_n e^{n j\omega t}$
\\\\
First multiply both sides by $e^{-(j\omega k t)}$, where $k\in \mathbb{Z}$. And integrate both sides over a given period, from $-\pi$ to $\pi$:

\begin{align} \label{eq:firststep_fouriercoefficient}
	\int_{-\pi}^\pi f(t)e^{-(j\omega k t)} = \int_{-\pi}^\pi \sum_{n=-\infty}^{\infty} c_n e^{n j\omega t} e^{-j\omega k t} dt
\end{align}
The integration of a $2\pi$ - periodic function over the length of the period, can be shifted with an integer.

\begin{lemma}\label{lemma:2pi-periodic_function}
Suppose $F$ is $2\pi$ - periodic and integrable. Then for any real number a 

\begin{align}
\int_a^{2\pi+a}F(t) dt = \int_0^{2\pi}F(t)dt
\end{align}
\end{lemma}
\begin{proof}
\begin{align*}
	\int_0^{2\pi}F(t)dt 
	&= \int_0^a F(t) dt + \int_a^{2\pi} 
	= \int_0^a F(t+2\pi)dt + \int_a^{2\pi} F(t) dt\\ 
	&= \int_{2\pi}^{2\pi + a} F(t) dt + \int_a^{2\pi}F(t)dt
	= \int_a^{2\pi}F(t)dt	+ \int_{2\pi}^{2\pi + a} F(t)dt \\
	&= \int_a^{2\pi+a}F(t)dt
\end{align*}
\end{proof}
Pulling the summation and the constant on the right-hand side out of the integral in \eqref{eq:firststep_fouriercoefficient} yields the following:
\begin{align*}
	\int_{-\pi}^\pi f(t) e^{-j \omega k t}dt
	= \sum_{-\infty}^\infty c_n \int_{\pi}^\pi e^{-j \omega(n-k)t}dt
\end{align*} 
The integral on the right-hand side has two cases to consider, $n \neq k$ and $n = k$\\\\
For $n\neq k$:
\begin{align*}
	\forall n,n\neq k: \int_{-\pi}^\pi e^{j\omega(n-k)t}dt 
	=\dfrac{1}{j\omega(n-k)}e^{j\omega(n-k)t}\mid_{-\pi}^{\pi}
	=\dfrac{(-1)^{n-k}-1(-1)^{n-k}}{j\omega(n-k)}
	=0
\end{align*}
\chr{Could be written with sine and cosine, to show that the integral of those 2 over a periode is 0}
The second case is for $n = k$
\begin{align*}
	\forall n,n=k: \int_{-\pi}^\pi e^{j\omega(n-k)t}dt = \int_{-\pi}^\pi dt = 2\pi
\end{align*}
The integral can be concluded to yield either $0$ or $2\pi$:
\begin{align}
	\int_{-\pi}^{\pi} e^{j \omega (n-k)t}dt 
	= 
	\begin{cases}
			2\pi \text{ if } n=k\\
			0 \text{ otherwise}
	\end{cases}
\end{align}
The coefficient $c_n$'s general equation is then:
\begin{align*}
	c_n = \dfrac{1}{2\pi} \int_{-\pi}^{\pi} f(t) e^{-(j \omega nt)}dt
\end{align*} 
\begin{definition} \label{def:fourier_definition}
Fourier series of a $2\pi$ - periodic integrabel function $f(t)$ is defined as:
\begin{align*}
	\sum_{n=-\infty}^\infty c_n e^{j n \omega t}
\end{align*}
where $c_n = \dfrac{1}{2\pi}\int_{- \pi}^\pi f(t) e^{-j n \omega t}$
\\\\
Alternatively:
\begin{align*}
	\dfrac{a_0}{2} + \sum_{n=1}^{\infty} \left[ a_n \cos(n \omega t) + b_n \sin(n \omega t)\right]
\end{align*} 
where
\begin{align*}
	a_n 
	&= \dfrac{1}{\pi} \int_{-\pi}^\pi f(t) \cos (n \omega t) dt, \, n=0,1,\dots\\
	b_n
	&= \dfrac{1}{\pi} \int_{-\pi}^\pi f(t) \sin (n \omega t) dt, \, n=1,2,\dots	
\end{align*}
\end{definition}
Further if a function $g(t)$ is uneven, ($g(t) = -g(-t)$), then the integral $\int_{-\pi}^\pi g(t) = 0$.
\subsection{Convergence of the Fourier series}
For a $2\pi$- periodic and integrabel function, the n'th. order Fourier partial-sum is defined by: 
\begin{align}\label{eq:partialsumFourierSeries}
	S_N^f(t) = \dfrac{1}{2} a_0 + \sum_1^N\left(a_n \cos n\omega t + b_n \sin n \omega t \right) = \sum_{-N}^N c_n e^jn\omega t
\end{align}
with the coefficients $a_n$ and $b_n$ or $c_n$ defined as in \ref{def:fourier_definition}.\\
\\
Inserting $c_n$ in the partial sum using $x$ in place of the variable $t$.
\begin{align*}
	S_N^f(t)
	= \dfrac{1}{2\pi}\sum_{-N}^N \int_{-\pi}^\pi f(x) e^{-j n \omega x} dx\, e^{jn\omega t}\\
	= \dfrac{1}{2\pi}\sum_{k = -N}^N \int_{-\pi}^\pi f(x) e^{j k \omega (x-t)} d(x)
\end{align*}
Notice that 
\begin{align*}
	S_N^f (t) 
	&= \dfrac{1}{2\pi} \sum_{n=-N}^N \int_{-\pi}^\pi f(x)e^{jn\omega(x-t)} dx\text{, and let } 
	\tau 
	= x-t\\
	&= \dfrac{1}{2\pi} \sum_{n = -N}^N \int_{-\pi - x}^{\pi - x} f(x + \tau ) e^{j n\omega \tau} d\tau
\end{align*}
By \ref{lemma:2pi-periodic_function} the above equation can be expressed as followed:
\begin{align*}
	S_N^f (\omega t) 
	&= \dfrac{1}{2\pi} \sum_{n=-N}^N \int_{-\pi}^\pi f(t + \tau) e^{jn \omega t} d\tau\\
	&= \int_{-\pi}^\pi f(t + \tau) D_N(\tau) d\tau
\end{align*}
Where $D_N = \dfrac{1}{2\pi}\sum_{n=-N}^{N}e^omega{jn\\tau}$ is a Dirichlet-core. 
The integral from $-\pi$ to $\pi$ of a Dirichlet-core is $\dfrac{1}{2}$ \chr{(Ref bogen for at undgå at snakke om Dirichlet kernen (kunne evt. vises ud fra Mortens noter)}
Using this information the follwing can be derived:
\begin{theorem}
	Let $f(t)$ be a $2\pi$-periodic and piece wise smooth then the limit of the partial sum $S_N^f$ is given by:
	 \begin{align*}
	 	\lim_{N\to\infty} S_N^f (t) = \dfrac{1}{2}\left[f(t-) + f(t+)\right], \, t\in [-\pi, \pi]
	 \end{align*}
	If $f$, is continues in $t$, then:
	\begin{align*}
		\lim_{N\to \infty} S_N^F(t) = f(t).
	\end{align*}
\end{theorem}
\begin{proof}
	\begin{align*}
	\dfrac{1}{2} f(\theta-) = f(\theta-) \int_{-\pi}^0 D_n(\tau)d\tau \text{ and } \dfrac{1}{2}f(\theta+) = f(\theta+) \int_0^\pi D_n (\tau)d\tau
	\end{align*}
	Which gives
\end{proof}
%%%%%%
More precisely, $f\in PS(a,b)$ iff 
\begin{enumerate}
	\item $f \in PC(a,b)$
	\item $f'$ exists and is continuous on $(a,b)$ except perhaps at finitely many points $x_1,\dots,x_k$ (which will include any points where f is discontinuous), and the one-sided limits $f'(x_j-)$ and $f'(x_j+)(j)1,\dots,K)$, and also $f'(a+)$ and $f'(b-)$, exist.
\end{enumerate}
The sum of any infinite series is defined to be the limit of its partial sums.
The N partial sum of the Fourier series be defined as:
\begin{align}\label{eq:partialsumFourierSeries}
	S_N^f(\omega t) = \dfrac{1}{2} a_0 + \sum_1^N\left(a_n \cos n\omega t + b_n \sin n \omega t \right) = \sum_{-N}^N c_n e^jn\omega t
\end{align}
Wants to show that the partial sum \eqref{eq:partialsumFourierSeries} converges.
Inserting the definition $a_n$ and $b_n$ or $c_n$ coefficients into \eqref{eq:partialsumFourierSeries} yields:
\begin{align*}
	S_N^f(\omega t) = \dfrac{1}{2\pi} \sum_{-N}^N \int_{-\pi}^\pi 
\end{align*}
%http://cnx.org/contents/8YnJdzjg@8/Derivation-of-Fourier-Coeffici

%Note to self foldning.